---
title: "COVID-19 Daily Count from LA Times"
Date: March 23 2021
author: "Abigail Horn"
output: html_document
chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#Load Libraries


```{r}
library(tidyr)
library(dplyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(ggplot2)
library(lubridate)
library(data.table)

library(MASS)
library(reshape2)
library(reshape)

library(network)

library(tidygraph)
library(ggraph)
library(plotly)
library(visNetwork)
library(networkD3)
library(here)

lab.dir <- here("static/slides/11-interactive-viz/lab/")

```


#Load data
```{r}

case_data <- fread("https://raw.githubusercontent.com/datadesk/california-coronavirus-data/master/latimes-place-totals.csv ")
case_data<-as.data.frame(case_data)
```



```{R}
case_data <- subset(case_data, county == "Los Angeles")
case_data$date <- as.Date(case_data$date)
case_data$name <- as.character(case_data$name)
data <- case_data
```

#Create daily table total

```{r}

summary.LA <- data %>%
 group_by(date) %>% 
 summarise(confirmed_cases = sum(confirmed_cases)) %>%
 ungroup()

summary.LA

summary.LA = summary.LA %>%
  arrange(date) %>%  # first sort by day
  mutate(Diff_day = date - lag(date),  # Difference in time (just in case there are gaps)
         new_cases = confirmed_cases - lag(confirmed_cases)) # Difference in case between days 

summary.LA

```


#Create daily table per City

```{r}

summary.city <- data %>%
 group_by(date, name) %>% 
 summarise(confirmed_cases = sum(confirmed_cases)) %>%
 ungroup()

summary.city

```


#Add number of new case per city

```{r}

summary.city = summary.city %>%
  group_by(name) %>%
  arrange(date) %>%  # first sort by day
  mutate(Diff_day = date - lag(date),  # Difference in time (just in case there are gaps)
         new_cases = confirmed_cases - lag(confirmed_cases)) %>% # Difference in case between days 
 arrange(name)

summary.city

```


## Plots {.tabset}

### LA County

```{r}

LA.plot <- ggplot(data = summary.LA, aes(x = date, y = confirmed_cases)) + 
  geom_line()

ggplotly(LA.plot)

```
#

### By City

```{r}
City.plot <- ggplot(data = subset(summary.city, name %in% c("Woodland Hills", "Sierra Madre")), aes(x = date, y = new_cases, color = name)) +
  geom_line()

ggplotly(City.plot)



#
City.plot <- ggplot(data = summary.city, aes(x = date, y = new_cases, color = name)) +
  geom_line()

ggplotly(City.plot)


```

{-}

#Step 3: Plot COVID-19 infections by neighborhood
● Read-in the COVID-19 infection data by neighborhood using my code “readin_COVID_data.Rmd” (in the COVID19_data folder)
   
   ○ The code will read-in the COVID-19 data for each neighborhood from the LA Times, and calculate the number of new infections each day from the number of cumulative infections

● Calculate for    week the 7-day new infection incidence rate per 100,000 population (“1-week crude IR”), i.e.
  ○ 1-week crude IR = [ sum(new infections in location i during 7 days) / population of I ] * 100,000 ● For each of the 8 weeks, plot the map of each neighborhood colored by the value of the 1-week crude
IR

###解释：
代码用于从 累计infectious中 计算出的每日感染者   ：data： LA每日不同city的情况：confirmed_cases、population
原数据是daily数据---


summary.LA ： LA层面，每日新增。（confirmed_cases、new_cases）   --------》LA.plot
summary.city ： city层面，每日新增。（name/city 、confirmed_cases、new_cases ） ------》City.plot 

LA 88个cities ，和超过400个neighbors？？
为何结果是352？？



```{R}

#data
#summary.LA
#summary.city
##去重计数：n_distinct()

n_distinct(data$name)

unique(data)
```




```{r}

#write_csv(data, "data.csv")

```
